\todo{Title} Sufficient conditions for reachability in automat networks with priorities

### 2014-03-19 main.tex
change title + todo in abstract

\begin{document}
\begin{frontmatter}
\title{Under-approximation of Reachability in Multivalued Asynchronous Networks}

@@

\begin{abstract}
The Process Hitting is a recently introduced framework designed for the modelling of concurrent systems.
Its originality lies in a compact representation of both components of the model and its corresponding actions:
each action can modify the status of a component, and is conditioned by the status of at most one other component.
This allowed to define very efficient static analysis based on local causality to compute reachability properties.
However, in the case of cooperations between components (for example, when two components are supposed to interact with a third one only when they are in a given configuration), the approach leads to an over-approximated interleaving between actions, because of the pure asynchronous semantics of the model.

>>>>

\begin{document}
\begin{frontmatter}
\title{\todo{Title} Sufficient conditions for reachability in automat networks with priorities}
%\title{Under-approximation of Reachability in Multivalued Asynchronous Networks}

@@

\begin{abstract}
\todo{Add flattening}
The Process Hitting is a recently introduced framework designed for the modelling of concurrent systems.
Its originality lies in a compact representation of both components of the model and its corresponding actions:
each action can modify the status of a component, and is conditioned by the status of at most one other component.
This allowed to define very efficient static analysis based on local causality to compute reachability properties.
However, in the case of cooperations between components (for example, when two components are supposed to interact with a third one only when they are in a given configuration), the approach leads to an over-approximated interleaving between actions, because of the pure asynchronous semantics of the model.
